---
pagetitle: Blog-roll
title: '{{< iconify gridicons reblog >}} Follow and learn'
theme: blog-roll.scss

execute: 
  echo: false
---

```{r "render_blog_feed() function"}

# A function to read in a list of blog posts from an RSS feed and output html
render_blog_feed <- function(
  feed_url,
  show_description = FALSE,
  max_chars = 200,
  n_items = 3
) {
  feed <- tryCatch(tidyRSS::tidyfeed(feed_url), error = function(e) NULL)

  if (is.null(feed)) {
    return(htmltools::tags$p("Feed unavailable."))
  }

  feed_items <- utils::head(feed, n_items)

  entries <- lapply(seq_len(nrow(feed_items)), function(i) {
    item <- feed_items[i, ]

    date_str <- format(as.Date(item$item_pub_date), "%e %B %Y")

    # Get description/first few lines of each post, truncate to maximum characters
    description <- if (show_description) {
      desc <- xml2::xml_text(xml2::read_html(paste0(
        "<x>",
        item$item_description,
        "</x>"
      )))
      desc <- gsub("<[^>]+>", "", desc)
      if (nchar(desc) > max_chars) {
        paste0(substr(desc, 1, max_chars), "...")
      } else {
        desc
      }
    } else {
      NULL
    }

    # Build list item
    htmltools::tagList(
      htmltools::tags$li(
        htmltools::HTML(paste0(
          "<strong>",
          date_str,
          "</strong>: ",
          "<a href='",
          item$item_link,
          "'>",
          item$item_title,
          "</a>"
        )),
        if (!is.null(description)) htmltools::tags$div(description)
      )
    )
  })

  htmltools::tags$ul(
    class = "blog-feed-list",
    entries
  )
}
```

```{r "render_blog_feed_dd() function"}

# A function to read in a list of blog posts from an RSS feed and output html with a hidden drop-down tag
render_blog_feed_dd <- function(
  feed_url,
  show_description = FALSE,
  max_chars = 200,
  n_items = 3,
  label = "Recent posts"
) {
  feed <- tryCatch(tidyRSS::tidyfeed(feed_url), error = function(e) NULL)
  if (is.null(feed)) {
    return(htmltools::tags$p("Feed unavailable."))
  }

  feed_items <- utils::head(feed, n_items)

  entries <- lapply(seq_len(nrow(feed_items)), function(i) {
    item <- feed_items[i, ]

    date_str <- format(as.Date(item$item_pub_date), "%e %B %Y")

    description <- if (show_description) {
      desc <- xml2::xml_text(xml2::read_html(paste0(
        "<x>",
        item$item_description,
        "</x>"
      )))
      desc <- gsub("<[^>]+>", "", desc)
      if (nchar(desc) > max_chars) {
        paste0(substr(desc, 1, max_chars), "...")
      } else {
        desc
      }
    } else {
      NULL
    }

    htmltools::tags$li(
      htmltools::HTML(paste0(
        "<strong>",
        date_str,
        "</strong>: ",
        "<a href='",
        item$item_link,
        "'>",
        item$item_title,
        "</a>"
      )),
      if (!is.null(description)) htmltools::tags$div(description)
    )
  })

  htmltools::tags$details(
    htmltools::tags$summary(label),
    htmltools::tags$ul(
      class = "blog-feed-list",
      c(
        entries,
        list(
          htmltools::tags$li(
            style = "list-style: none; font-style: italic; margin-top: 0.5em;",
            paste0(
              "(Last rendered on ",
              format(Sys.time(), "%e %B %Y at %R"),
              ")"
            )
          )
        )
      )
    )
  )
}
```


::::::::::::::::::::: grid
:::: {.g-col-12 .g-col-sm-6 .g-col-md-4}
::: heading-row
### Quantitude

{{< var podcast >}}
:::

This is a must listen! The [Quantitude podcast](https://quantitudepod.org/) co-hosted and masterfully produced by Patrick Curran (UNC\@CH) and Greg Hancock (UMD) is proof that great comedy can also be done sitting down and despite mastering only a bad pirate accent and being of Transylvanian lineage (😎). And it's about quantitative methods and academia. The dudes are seriously flawed, though; they're likelihoodists who get a kick out of calling up Bayesians at 5:40 in the morning asking them to explain themselves.

```{r}
render_blog_feed_dd("https://feeds.buzzsprout.com/639103.rss", label = "Recent pods")
```
::::

:::: {.g-col-12 .g-col-sm-6 .g-col-md-4}
::: heading-row
### Andrew Gelman et al.

{{< var blog >}}
:::

You know this one. Running since 2004, the [Statistical Modeling, Causal Inference, and Social Science](https://statmodeling.stat.columbia.edu/) blog coordinated by statistician and political scientist Andrew Gelman (Columbia) - but also contributed to by an increasing number of his collaborators - functions like a statistics consultancy desk for the world. Andrew is probably the most influential voice for pragmatic Bayesianism in the social sciences, and a prolific textbook author who has gifted treasures to quantitative educators worldwide.

```{r}
render_blog_feed_dd("https://statmodeling.stat.columbia.edu/feed/")
```
::::

:::: {.g-col-12 .g-col-sm-6 .g-col-md-4}
::: heading-row
### Richard McElreath

{{< var blog >}}
:::

Richard is best known outside the field of evolutionary anthropology for his foundational Bayesian textbook [Statistical Rethinking](https://xcelab.net/rm/) and related [YouTube course lectures](https://youtube.com/playlist?list=PLDcUM9US4XdPz-KxHM4XHt7uUVGWWVSus&si=ZTiq6snAUOutn8Em). Currently directing a Max Planck Institute in Leipzig, his blog [Elements of Evolutionary Anthropology](https://elevanth.org/blog/) is not extremely active, but it makes up for that with the quality of the thoughts conveyed in each post.

```{r}
render_blog_feed_dd("https://elevanth.org/blog/feed/")
```
::::

:::: {.g-col-12 .g-col-sm-6 .g-col-md-4}
::: heading-row
### Andrew Heiss

{{< var blog >}}
:::

Andrew Heiss is a political scientist and public policy researcher at GSU. He has the strongest [explicit commitment to making all aspects of his work open and transparent](https://talks.andrewheiss.com/2022-03-22_uga-putting-everything-out-there/slides.html#1) that you'll find anywhere on the internet today. [His blog](https://www.andrewheiss.com/blog/) dives deeply into various technical aspects of social science programming and it's a wonderful resource for learning about coding in R.

```{r}
render_blog_feed_dd("https://www.andrewheiss.com/atom.xml")
```
::::

:::: {.g-col-12 .g-col-sm-6 .g-col-md-4}
::: heading-row
### Learning Bayesian Statistics

{{< var podcast >}} {{< var videocast >}}
:::

Hosted by Alexandre Andorra, a Bayesian modeller at PyMC Labs, the [Learning Bayesian Statistics](https://learnbayesstats.com/episodes) podcast focuses on long-form conversations with various people who have contributed to Bayesian modelling in various academic fields and industries. Some recent episodes have a hybrid workshop format with a videocast available on the series' [YouTube channel](https://www.youtube.com/@learningbayesianstatistics/videos).

```{r}
render_blog_feed_dd("https://feeds.captivate.fm/learnbayesstats", label = "Recent pods")
```
::::

:::: {.g-col-12 .g-col-sm-6 .g-col-md-4}
::: heading-row
### Data Is Plural

{{< var newsletter >}} {{< var podcast >}}
:::

[Data Is Plural](https://www.data-is-plural.com/) is a long-running newsletter curated by Jeremy Singer-Vine, currently a data editor for the New York Times (previously at *BuzzFeed*, *The Wall Street Journal* and *Slate*). It's a good idea to subscribe to the newsletter to receive a list of interesting and useful publicly available datasets every once in a while, which are also added to a [Google Docs spreadsheet](https://docs.google.com/spreadsheets/d/1wZhPLMCHKJvwOkP4juclhjFgqIY8fQFMemwKL2c64vk/edit?gid=0#gid=0) containing all the datasets listed in past editions of the newsletter. It also has an [associated podcast](https://podcast.data-is-plural.com/2159594/episodes), although that has been quiet recently.

```{r}
render_blog_feed_dd("https://data-is-plural.github.io/newsletter-archive/feeds/dip.rss", label = "Recent newsletters", show_description = TRUE)
# render_blog_feed_dd("https://feeds.buzzsprout.com/2159594.rss", label = "Recent pods")
```
::::

:::: {.g-col-12 .g-col-sm-6 .g-col-md-4}
::: heading-row
### Frank Harrell

{{< var blog >}}
:::

Frank Harrell is Professor of Biostatistics at Vanderbilt University and is known in the R community for his popular R packages. His blog [Statistical Thinking](https://www.fharrell.com/post/) has been going since 2017 and contains very useful posts on various statistical tests and models implemented in R.

```{r}
render_blog_feed_dd(
  "https://www.fharrell.com/index.xml"
)
```
::::

:::: {.g-col-12 .g-col-sm-6 .g-col-md-4}
::: heading-row
### Danielle Navarro

{{< var blog >}}
:::

I first encountered Danielle's work as the author of a very lucid online textbook on [Learning Statistics with R](https://learningstatisticswithr.com/) from back when she was a lecturer in quantitative psychology at the University of Adelaide. She has since moved into industry and has developed many cool interests in computational methods (including [generative art](https://art.djnavarro.net/)). Her data science blog [Notes from a data witch](https://blog.djnavarro.net/) is a treasure trove.

```{r}
render_blog_feed_dd(
  "https://blog.djnavarro.net/index.xml"
)
```
::::

:::: {.g-col-12 .g-col-sm-6 .g-col-md-4}
::: heading-row
### Kieran Healy

{{< var blog >}}
:::

Fellow sociologist Kieran Healy (Duke) is a prolific author on both substantive and technical topics. He has written on almost everything from [organ procurement](https://kieranhealy.org/publications/lbg/), through [the institutionalization of mass shootings](https://kieranhealy.org/publications/rituals-of-childhood/) as a ritual of American childhood, to the problems of [digital capitalism](https://kieranhealy.org/publications/tos/). His [Plain Person's Guide to Plain Text Social Science](https://kieranhealy.org/files/papers/plain-person-text.pdf) has been a terrific resource for those transitioning to computationally reproducible research workflows, and he is best known in the R social science community for his book on [Data Visualization](https://socviz.co/). His [blog](https://kieranhealy.org/blog/) is just as diverse and interesting.

```{r}
render_blog_feed_dd(
  "https://kieranhealy.org/blog/index.xml"
)
```
::::
:::::::::::::::::::::